Enrich the datasets with new columns.

### 2020-08-28 inst/analysis/enrich_dataset.Rmd
AST Size on all the dataset!
Fix call sites per package

@@

@@

```{r write_back}
write_fst(undefined_per_package, PACKAGE_EVALS_DYNAMIC_FILE)

>>>>

```{r}
eval_calls_ast_size <- eval_calls_corpus %>% select(eval_call_srcref, caller_package, caller_function, eval_source_type, expr_resolved_nodes, nb_ev_calls)

write_fst(eval_calls_ast_size, path(RUN_TRACE_DIR, "summarized-ast-size.fst"))
```

@@

# Known call sites per packages

```{r defined_call_sites}
call_sites_per_package <- eval_calls_corpus %>% 
    filter(eval_source_type == "package", eval_source %in% corpus_files) %>%
    group_by(eval_source) %>%
    summarize(n = n_distinct(eval_call_srcref))

known_packages <- setdiff(corpus_files, call_sites_per_package$eval_source) %>% as_tibble_col(column_name = "eval_source")

known_packages <- known_packages %>% mutate(n = 0)

call_sites_per_package <- bind_rows(call_sites_per_package, known_packages) %>%
  rename(package = eval_source) %>% 
  arrange(desc(n))

write_fst(call_sites_per_package, PACKAGE_EVALS_DYNAMIC_FILE)

```{r}
max_call_sites <- max(call_sites_per_package$n)
r("max call sites enrich")
```

@@

```{r write_back}
write_fst(undefined_per_package, PACKAGE_EVALS_UNDEFINED_FILE)
